


\documentclass[preprint]{elsarticle}

\begin{document}


To:
Journal of Applied Physics Editorial Board


Subject:
Article Submit

\vspace{5mm}
Dear Editors,

\vspace{3mm}
%Enclosed is a manuscript entitled “XXX XXXX XXXXX” by sb, which we are submitting for publication in the journal of …. We have chosen this journal because it deals with …
Enclosed with this letter you will find the electronic submission of manuscript entitled
``Microwave induced transformation of defect in SiC and GaAs'' O.~Olikh  and P.~Lytvyn.
This is an original paper which has not been simultaneously submitted as a whole or in part anywhere else.
No conflict of interest exits in the submission of this manuscript.


It is well known that defects are crucial for the semiconductor structure performance.
As a result, the methods aimed at
modifying the system of defects are very important for practical applications.
The influence of certain factors, for example, radiation, has been studied quite well.
At the same time, new agents begin to attract more attention, such as ultrasound loading
or microwave treatment (MWT).
The present manuscript describes
 MWT impact on the parameters of deep centers located in the near surface region of $n$–-6H-–SiC and $n$-–GaAs single crystals,
as well as on  GaAs  epitaxial structures.
We believe that such way of defect modification would be of interest to the readers.

We would  very much appreciate if you would consider the manuscript for publication in the \emph{Journal of Applied Physics}.
%We appreciate your consideration of our manuscript, and we look forward to receiving comments from the reviewers.

\vspace{3mm}

Sincerely yours,

Oleg~Olikh and Petro~Lytvyn.

E-mail: olegolikh@knu.ua


%Dear Editors
%It is more than 12 weeks since I submitted our manuscript (No: ) for possible publication in your journal. I have not yet received a reply and am wondering whether you have reached a decision. I should appreciated your letting me know what you have decided as soon as possible.








\end{document}

