


\documentclass[preprint]{elsarticle}

\begin{document}


To:
Semiconductor Science and Technology Editorial Board


Subject:
Article Submit

\vspace{5mm}
Dear Editors,

\vspace{3mm}
%Enclosed is a manuscript entitled “XXX XXXX XXXXX” by sb, which we are submitting for publication in the journal of …. We have chosen this journal because it deals with …
Enclosed with the letter, you will find the electronic submission of the manuscript entitled
``Defect engineering using microwave processing in SiC and GaAs'' O.~Olikh  and P.~Lytvyn.
It is an original paper that has not been simultaneously submitted as a whole or in part anywhere else.
No conflict of interest exists in the submission of this manuscript.


The defects are known to be crucial for the semiconductor structure performance.
As a result, the methods intended to modify the system of defects are very important for practical applications.
The influence of certain factors, for example, radiation, has been studied quite well.
At the same time, new agents begin to attract more attention, such as ultrasound loading
or microwave treatment (MWT).
The present manuscript describes the effect of MWT on the parameters of deep centers located in the near-surface region
of single crystals $n$-6H–SiC, $n$-GaAs, and epi-GaAs epitaxial structures.
In particular the abruption of interstitial atoms are revealed.
We believe that such a way of defect engineering would be of interest to the readers.

We would  very much appreciate it if you would consider the manuscript for publication in the \emph{Semiconductor Science and Technology}.
%We appreciate your consideration of our manuscript, and we look forward to receiving comments from the reviewers.

\vspace{3mm}

Sincerely yours,

Oleg~Olikh and Petro~Lytvyn.

E-mail: olegolikh@knu.ua


%Dear Editors
%It is more than 12 weeks since I submitted our manuscript (No: ) for possible publication in your journal. I have not yet received a reply and am wondering whether you have reached a decision. I should appreciated your letting me know what you have decided as soon as possible.








\end{document}

