


\documentclass[preprint]{elsarticle}

\begin{document}


To:
Superlattices and Microstructures Editorial Board


Subject:
Article Submit

\vspace{5mm}
Dear Editors,

\vspace{3mm}
%Enclosed is a manuscript entitled “XXX XXXX XXXXX” by sb, which we are submitting for publication in the journal of …. We have chosen this journal because it deals with …
Enclosed with this letter you will find the electronic submission of manuscript entitled
``Deep neural network method for predicting the iron concentration in silicon solar cell by current-voltage characteristic'' O.~Olikh, O.~Lozitsky, and O.~Zavhorodnii.



This is an original paper which has not been simultaneously submitted as a whole or in part anywhere else.
No conflict of interest exits in the submission of this manuscript.


It is well known that impurities are crucial for the solar cells performance.
There are many experimental methods for impurity evaluation, such as the infrared spectroscopy, deep level transient spectroscopy, photoluminescence, thermally stimulated capacitance and current, secondary ion mass spectrometry etc.
These methods are complicated enough and demand a special setup.
At the same time, there is a simpler and commonly used technique, which
is the analysis of the solar cell current--voltage characteristics.
The present manuscript describes the method of contaminant concentration evaluation by
using the ideality factor value, which extracted from current-voltage curve.
The method is based on results of numerical simulation of solar cells and use a deep neural network. 
We believe that such way of defect characterisation would be of interest to the readers.

We would  very much appreciate if you would consider the manuscript for publication in the \emph{Superlattices and Microstructures}.
%We appreciate your consideration of our manuscript, and we look forward to receiving comments from the reviewers.

\vspace{3mm}

Sincerely yours,

Oleg~Olikh and co-authors


Taras Shevchenko National University of Kyiv


Kyiv 01601, Ukraine

E-mail: olegolikh@knu.ua


%Dear Editors
%It is more than 12 weeks since I submitted our manuscript (No: ) for possible publication in your journal. I have not yet received a reply and am wondering whether you have reached a decision. I should appreciated your letting me know what you have decided as soon as possible.








\end{document}

