


\documentclass[preprint]{elsarticle}

\begin{document}


To:
Semiconductor Science and Technology Editorial Board


Subject:
Article Submit

\vspace{5mm}
Dear Editor,

\vspace{3mm}
We are pleased to submit our manuscript entitled
“Computer vision-based method for quantifying iron-related defects in silicon solar cell”
for consideration for publication in Semiconductor Science and Technology
(Focus Collection on Defects in Semiconductors).


Defects in semiconductor and functional materials critically influence their electrical, optical, and catalytic properties. 
Therefore, developing reliable and quantitative methods for their characterization is of fundamental and technological importance. 
Machine learning offers powerful tools for analyzing complex microstructural features, 
yet its application is often limited by the lack of sufficiently large experimental datasets.

In this work, we demonstrate that transfer learning from pretrained computer vision models 
enables accurate quantitative prediction and characterization of defect-related features 
even from extremely small experimental datasets. 
We explored various image-based descriptors as inputs to regression models and assessed their predictive performance. 
Our results show that transfer learning allows extraction of meaningful information 
about defects from images and supports reliable regression of experimentally measured quantities. 
This provides a data-efficient strategy for defect characterization in semiconductors and related materials.

In our view, this study aligns with the aims of the Focus Collection, 
addressing both the scientific challenge of defect analysis 
and the development of innovative machine learning–based methodologies for materials characterization.


We confirm that this manuscript has not been published previously 
and is not under consideration by any other journal. 
No conflict of interest exists in the submission of this manuscript.
All authors have approved the final version of the manuscript.

Thank you for considering this manuscript. We look forward to your evaluation.

%We would  very much appreciate it if you would consider the manuscript for publication in the \emph{Semiconductor Science and Technology}.
%We appreciate your consideration of our manuscript, and we look forward to receiving comments from the reviewers.

\vspace{3mm}

Sincerely yours,

Oleg~Olikh, 

Oleksii Zavhorodnii, 

and Yulia Perets


E-mail: olegolikh@knu.ua


%Dear Editors
%It is more than 12 weeks since I submitted our manuscript (No: ) for possible publication in your journal. I have not yet received a reply and am wondering whether you have reached a decision. I should appreciated your letting me know what you have decided as soon as possible.








\end{document}

