


\documentclass[preprint]{elsarticle}

\begin{document}


To:
Superlattices and Microstructures Editorial Board


Subject:
Article Submit

\vspace{5mm}
Dear Editors,

\vspace{3mm}
%Enclosed is a manuscript entitled “XXX XXXX XXXXX” by sb, which we are submitting for publication in the journal of …. We have chosen this journal because it deals with …
Enclosed with this letter you will find the electronic submission of manuscript entitled
``Relationship between the ideality factor and the iron concentration in silicon solar cells'' by Oleg Olikh.



This is an original paper which has not been simultaneously submitted as a whole or in part anywhere else.
No conflict of interest exits in the submission of this manuscript.


The first version of manuscript was rejected by Dr.~Ma, Managing Editor because
the level of English has not meet the journal's standard.
I am sorry for English. 
I consulted a professional language editing service, the text was revised and I hope for language improving.


It is well known that impurities are crucial for the solar cells performance.
There are many experimental methods for solving this problem, such as the infrared spectroscopy, deep level transient spectroscopy, photoluminescence,
thermally stimulated capacitance and current, secondary ion mass spectrometry etc.
These methods are complicated  enough and demand a special setup.
At the same time, there is a simpler and more commonly used technique, which is the analysis of the solar cell current--voltage characteristics.
The present manuscript describes the method of contaminant concentration evaluation by using the ideality factor value, which extracted from current--voltage curve.
The method is based on results of numerical simulation of solar cells.
I believe that such way of defect characterisation would be of interest to the readers.


I would  very much appreciate if you would consider the manuscript for publication in the \emph{Superlattices and Microstructures}.
%We appreciate your consideration of our manuscript, and we look forward to receiving comments from the reviewers.

\vspace{3mm}

Sincerely yours,

Oleg~Olikh


Taras Shevchenko National University of Kyiv


Kyiv 01601, Ukraine

E-mail: olikh@univ.kiev.ua


%Dear Editors
%It is more than 12 weeks since I submitted our manuscript (No: ) for possible publication in your journal. I have not yet received a reply and am wondering whether you have reached a decision. I should appreciated your letting me know what you have decided as soon as possible.








\end{document}

